Fluid-mechanical erosion creates anisotropic porous media

### 2022-05-16 docs/PhysicsPaper/StokesErosion.tex
NM

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering \label{}
\includegraphics[width = 0.99 \textwidth]{./figs/fig2.pdf}
\caption{A single simulation of porous-medium erosion. The initial configuration consists of 80 circular bodies of random size and position, as seen in Fig.~1? a) As the medium erodes, the fraction of solid-body area decreases, or, equivalently, the porosity increases. b) Resistance to flow can be characterized by either the inverse permeability $1/k$ or the cumulative drag, the two of which are related through \eqref{ResistDrag}. Both are seen to decrease as the medium erodes, and relationship \eqref{ResistDrag} is confirmed by the simulation data.
c) The relationship between permeability $k$ and porosity $\phi$ for the eroding medium. Both quantities increase with time as the medium erodes, but at different rates due to changes in the microstructure and channelization of the medium.
}
\end{figure*}
%---------------------------------------------------------%

>>>>

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering \label{fig2}
\includegraphics[width = 0.99 \textwidth]{./figs/fig2.pdf}
\caption{A single simulation of porous-medium erosion. The initial configuration consists of 100 circular bodies of random size and position, as seen in Fig.~1? a) As the medium erodes, the fraction of solid-body area decreases, or, equivalently, the porosity increases. b) Resistance to flow can be characterized by either the inverse permeability, $1/k$, or the cumulative drag, the two of which are related through \eqref{ResistDrag}. Both are seen to decrease as the medium erodes, and relationship \eqref{ResistDrag} is confirmed by the simulation data.
c) The relationship between permeability $k$ and porosity $\phi$ for the eroding medium. Both quantities increase with time as the medium erodes, but at different rates due to changes in the microstructure and channelization of the medium.
}
\end{figure*}
%---------------------------------------------------------%
% Data from 100-3

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering \label{fig3}
\includegraphics[width = 0.99 \textwidth]{./figs/fig3.pdf}
\caption{
a)
}
\end{figure*}
%---------------------------------------------------------%
% Data from 100-3

Fig. 2 clearly shows a stark difference in the  permeability to flow in the horizontal versus vertical directions.

Text for Fig 3: 
The anisotropy of permeability grows large, up to a value of 4 during the middle portion of the simulation. The figure also shows the anisotropy of the circular grid.
